paper

### 2019-01-10 Report/paper.tex
push changes

    \documentclass[journal,onecolumn]{IEEEtran}
\usepackage[noadjust]{cite}

@@

    Since we don't have the same number of documents for each year we needed
to scale over the years and use the percentage of appearence of a word.
So after groupping the words by year and scaling them we found graph
below

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_26_0.png}\end{center}
        \caption{}
        \label{}
    \end{figure}

    We wanted then to know what are the trends of words for each specific
year, so we select distinct words for each year, it means that we select
for each year the words that were present for that year and never for
the others. We get the graph below. As we can see from the graph, the
most used word in the papers, more than 10\% of 2015 papers uses the
word `peer', more than 6\% of the papers uses the words `building',
`embodied' in 2016. In 2017 the most frequent keyword on is `reponsive'
and in 2018 `tools' is present with more than 6\%.

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_28_0.png}\end{center}
        \caption{}
        \label{}
    \end{figure}

@@

This method does not give good results as we can see it in the graph
below all the vectors are together there is no clear separation between
the documents. So we decide to use other methods using word embeddings
and properties of TF-IDF.

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_31_0.png}\end{center}
        \caption{}
        \label{}
    \end{figure}

@@

Once we get a document vector representation, we apply to it K-means.
The results are better, but we have only two clusters. If we increase
the number of clusters than there is no clear separation anymore
separation.

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_33_0.png}\end{center}
        \caption{}
        \label{}
    \end{figure}

@@

Once we get our new vector representation, we apply K-means and we get
the best separation, with a clear separation of 4 clusters as we can see
it in the figure below.

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_35_0.png}\end{center}
        \caption{}
        \label{}
    \end{figure}

@@

\begin{Verbatim}[commandchars=\\\{\}]
{\color{outcolor}Out[{\color{outcolor}212}]:} <IPython.core.display.HTML object>
\end{Verbatim}

    The resulted graph, is an undirected graph with 805 nodes and 6699
edges. On this graph we extract two main information : * Strongly
connected components to be able to detect clusters and related
documents. * In\_degree in order to check if there are documents that
are related to a lot of documents and those documents would be more
general than others, and won't necessarly belong to one specific
cluster.

@@

The second graph is more about the referenced documents and not about
the documents themselves. The aim of this graph is to see if there are
documents that are more likely to cited together. If it is the case,
then these documents are likely to be about the same subject. It is a
weighted graph constructed as follow: for each document, we create a
link between the references of the document. We create a dictionnary of
links, if the link is already in the dictionnary then we increase the
weight of the link. So for instance, if two references are present
together in the 5 distinct documents, then the weight of the edge would
be of 5. We obtain a graph of 10845 nodes and 148594 edges.

\begin{Verbatim}[commandchars=\\\{\}]
{\color{outcolor}Out[{\color{outcolor}103}]:} <IPython.core.display.HTML object>
\end{Verbatim}

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_44_0.png}\end{center}
        \caption{}
        \label{}
    \end{figure}

@@

\begin{Verbatim}[commandchars=\\\{\}]
{\color{outcolor}Out[{\color{outcolor}105}]:} <IPython.core.display.HTML object>
\end{Verbatim}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_50_0.png}\end{center}
        \caption{One of the connected components of the co-authorship graph}
        \label{fig_plot}
    \end{figure}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_52_0.png}\end{center}
        \caption{Largest Component}
        \label{author_collab_large}
    \end{figure}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_54_0.png}\end{center}
        \caption{Subcommunities by Louvain}
        \label{Louvain}
    \end{figure}

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_55_0.png}\end{center}
        \caption{Subcommunities via normalized cuts}
        \label{normalized}
    \end{figure}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_57_0.png}\end{center}
        \caption{Different formats used to reference institution}
        \label{unigraph}
    \end{figure}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_64_0.png}\end{center}
        \caption{Different formats used to reference institution}
        \label{figrep}
    \end{figure}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_66_0.png}\end{center}
        \caption{Collaborative papers between countries}
        \label{figcollab}
    \end{figure}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_68_0.png}\end{center}
        \caption{Movement of participants across institutions}
        \label{fig_move}
    \end{figure}

@@

The distribution of referenced publications years are plotted in the
graph below. We can see from the graph that there is a kind of a trend,
each two, three years there is a pick of documents referenced followed
by a two or three years of stagnancy. We can also notice that
throughouts the year each pick is higher than the older one, which can
be explained by the fact that The International Society of the Learning
Sciences community is investigating more and more tools to facilitate
learning over the years.

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_70_0.png}\end{center}
        \caption{}
        \label{}
    \end{figure}

    Since the number of documents is increasing over the years, we also
wanted to investigate more if the relevance of all the documents
published is increasing too. Using Pagerank algorithm and the In-degree
of each nodes to get the most influancial documents referenced of the
citation graph that we constructed (graph3) before. We filtered the
first 100 documents and then contructed a histogram of the counts. We
obtain the figure below:

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_72_0.png}\end{center}
        \caption{}
        \label{}
    \end{figure}

@@

    The top 10 of the most influencial and most important referenced papers
are the following:

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_75_0.png}\end{center}
        \caption{}
        \label{}
    \end{figure}

    We also noticed from the first graph that some documents were more
likely to cited together. We can say that the more two documents are
likely to cited together the more it is probable that both documents are
about the same subject From the table below we can also notice that some
papers cites like to cite the same authors together, which is logic in a
sense, because if some authors always treat about the same subjects then
they are experts in that field and a lot of their publications are
relevant and can be cited together.

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_77_0.png}\end{center}
        \caption{}
        \label{}
    \end{figure}

    Using this graph, we also want to extract if there are some clusters of
papers cited together. As we explained before, we run strongly connected
algorithm to check if some cited documents are more likely to cited
together, and this will give us clusters of cited documents that are
more likely to be about the same subjects. We can visualise one cluster,
the most important one.

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_80_0.png}\end{center}
        \caption{}
        \label{}
    \end{figure}

\begin{Verbatim}[commandchars=\\\{\}]
{\color{outcolor}Out[{\color{outcolor}185}]:} <IPython.core.display.HTML object>
\end{Verbatim}

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_82_0.png}\end{center}
        \caption{}
        \label{}
    \end{figure}

@@

\begin{Verbatim}[commandchars=\\\{\}]
{\color{outcolor}Out[{\color{outcolor}236}]:} <IPython.core.display.HTML object>
\end{Verbatim}

    In the table below are the documents of the giant connected component
represented in the interactive graph above.

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_86_0.png}\end{center}
        \caption{}
        \label{}
    \end{figure}

@@

So if more than 4 documents are referenced by two distinct documents
than the latter are more likely to be about the same subect.

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_88_0.png}\end{center}
        \caption{}
        \label{}
    \end{figure}

>>>>

    \documentclass[journal,twocolumn]{IEEEtran}
\usepackage[noadjust]{cite}

@@

    Since we don't have the same number of documents for each year we needed
to scale over the years and use the percentage of appearence of a word.
So after groupping the words by year and scaling them we found graph
below \ref{fig1}

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_26_0.png}\end{center}
        \caption{Trends of keywords over the years}
        \label{fig1}
    \end{figure}

    We wanted then to know what are the trends of words for each specific
year, so we select distinct words for each year, it means that we select
for each year the words that were present for that year and never for
the others. We get the figure below. As we can see from the graph
\ref{fig2}, the most used word in the papers, more than 10\% of 2015
papers uses the word `peer', more than 6\% of the papers uses the words
`building', `embodied' in 2016. In 2017 the most frequent keyword on is
`reponsive' and in 2018 `tools' is present with more than 6\%.

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_28_0.png}\end{center}
        \caption{Distinct keywords over the years}
        \label{fig2}
    \end{figure}

@@

This method does not give good results as we can see it in the graph
below \ref{fig3} all the vectors are together there is no clear
separation between the documents. So we decide to use other methods
using word embeddings and properties of TF-IDF.

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_31_0.png}\end{center}
        \caption{Baseline model document clusters}
        \label{fig3}
    \end{figure}

@@

Once we get a document vector representation, we apply to it K-means.
The results are better, but we have only two clusters. If we increase
the number of clusters than there is no clear separation anymore
separation. The plot below \ref{fig4} reprensents the documents
belonging to each cluster.

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_33_0.png}\end{center}
        \caption{Cluster using Average of GloVe vectors combined with K-means }
        \label{fig4}
    \end{figure}

@@

Once we get our new vector representation, we apply K-means and we get
the best separation, with a clear separation of 4 clusters as we can see
it in the figure below \ref{fig5}.

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_35_0.png}\end{center}
        \caption{Cluster using Weighted average of TF-IDF + GloVe  combined with K-means }
        \label{fig}
    \end{figure}

@@

    The resulted graph is plotted in this figure \ref{intersection}, is an
undirected graph with 805 nodes and 6699 edges. On this graph we extract
two main information : * Strongly connected components to be able to
detect clusters and related documents. * In\_degree in order to check if
there are documents that are related to a lot of documents and those
documents would be more general than others, and won't necessarly belong
to one specific cluster.

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_41_0.png}\end{center}
        \caption{Intersection between references graph}
        \label{intersection}
    \end{figure}

@@

The second graph is more about the referenced documents and not about
the documents themselves. The aim of this graph is to see if there are
documents that are more likely to cited together. If it is the case,
then these documents are likely to be about the same subject. It is a
weighted graph constructed as follow: for each document, we create a
link between the references of the document. We create a dictionnary of
links, if the link is already in the dictionnary then we increase the
weight of the link. So for instance, if two references are present
together in the 5 distinct documents, then the weight of the edge would
be of 5. We obtain a graph of 10845 nodes and 148594 edges represented
in this figure \ref{fig6}

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_45_0.png}\end{center}
        \caption{}
        \label{}
    \end{figure}

@@

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_51_0.png}\end{center}
        \caption{One of the connected components of the co-authorship graph}
        \label{fig_plot}
    \end{figure}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_53_0.png}\end{center}
        \caption{Largest Component}
        \label{author_collab_large}
    \end{figure}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_55_0.png}\end{center}
        \caption{Subcommunities by Louvain}
        \label{Louvain}
    \end{figure}

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_56_0.png}\end{center}
        \caption{Subcommunities via normalized cuts}
        \label{normalized}
    \end{figure}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_58_0.png}\end{center}
        \caption{Different formats used to reference institution}
        \label{unigraph}
    \end{figure}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_65_0.png}\end{center}
        \caption{Different formats used to reference institution}
        \label{figrep}
    \end{figure}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_67_0.png}\end{center}
        \caption{Collaborative papers between countries}
        \label{figcollab}
    \end{figure}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_69_0.png}\end{center}
        \caption{Movement of participants across institutions}
        \label{fig_move}
    \end{figure}

@@

The distribution of referenced publications years are plotted in the
graph \ref{count_ref_docs}. We can see from the graph that there is a
kind of a trend, each two, three years there is a pick of documents
referenced followed by a two or three years of stagnancy. We can also
notice that throughouts the year each pick is higher than the older one,
which can be explained by the fact that The International Society of the
Learning Sciences community is investigating more and more tools to
facilitate learning over the years.

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_71_0.png}\end{center}
        \caption{Distribution of the number of referenced documents belonging to each year}
        \label{count_ref_docs}
    \end{figure}

    Since the number of documents is increasing over the years, we also
wanted to investigate more if the relevance of all the documents
published is increasing too. Using Pagerank algorithm and the In-degree
of each nodes to get the most influancial documents referenced of the
citation graph that we constructed (graph3) before. We filtered the
first 100 documents and then contructed a histogram of the counts. We
obtain the figure \ref{fig7}:

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_73_0.png}\end{center}
        \caption{Distribution of the 100 most referenced documents belonging to each year}
        \label{fig7}
    \end{figure}

@@

    The top 10 of the most influencial and most important referenced papers
are represented in table \ref{indegree}:

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_76_0.png}\end{center}
        \caption{In-degree count for each document}
        \label{indegree}
    \end{figure}

    We also noticed from the first graph that some documents were more
likely to cited together. We can say that the more two documents are
likely to cited together the more it is probable that both documents are
about the same subject From the table \ref{fig8} we can also notice that
some papers cites like to cite the same authors together, which is logic
in a sense, because if some authors always treat about the same subjects
then they are experts in that field and a lot of their publications are
relevant and can be cited together.

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_78_0.png}\end{center}
        \caption{Count of documents cited together}
        \label{fig8}
    \end{figure}

    Using this graph, we also want to extract if there are some clusters of
papers cited together. As we explained before, we run strongly connected
algorithm to check if some cited documents are more likely to be cited
together, and this will give us clusters of cited documents that are
more likely to be about the same subjects. We can visualise one cluster,
the most important one.

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_81_0.png}\end{center}
        \caption{Table of the documents belonging to the same clusters}
        \label{fig9}
    \end{figure}

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_83_0.png}\end{center}
        \caption{}
        \label{}
    \end{figure}

@@

    In the table \ref{fig10} below are the documents of the giant connected
component represented in the interactive graph \ref{fig11}.

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_87_0.png}\end{center}
        \caption{Giant component graph}
        \label{fig12}
    \end{figure}

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_88_0.png}\end{center}
        \caption{Documents belonging to the giant component}
        \label{fig10}
    \end{figure}

@@

So if more than 4 documents are referenced by two distinct documents
than the latter are more likely to be about the same subect. In the
table \ref{fig11} we can find some of the papers that belong to the same
clusters.

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_90_0.png}\end{center}
        \caption{Documents in conferences belonging to the same clusters}
        \label{fig11}
    \end{figure}
